---
title: "Data analysis, the data.table way"
author: "Bijan Seyednasrollah"
date: "5/1/2020"
output: html_document
---

<!-- Global site tag (gtag.js) - Google Analytics -->
<script async src="https://www.googletagmanager.com/gtag/js?id=UA-30213986-7"></script>
<script>
  window.dataLayer = window.dataLayer || [];
  function gtag(){dataLayer.push(arguments);}
  gtag('js', new Date());

  gtag('config', 'UA-30213986-7');
</script>


```{r, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,  eval = TRUE)
knitr::purl('datatable.Rmd')
```


## Objectives

In this tutorial, you will learn:

1. what data.tables are,
2. why they are so powerful, and
3. how to work with them.

## Introduction

**_data.table_**'s are powerful data structures for storing tabular data in R. **_data.table_**'s may look similar to basic **_data.table_**'s, but they are much more powerful for not only storing data but also for performing on the fly data analyses and data queries **_data.table_**'s use high performance computing for fast and quick task accomplishments. 

You can download the [**_R_**](datatable.R) code and the [**_R Markdown_**](datatable.Rmd) document of this tutorial.

To work with **_data.table_**'s, first you need to install the **data.table** _R_ package.

```{r, eval=FALSE}
# install from CRAN
install.packages('data.table', repos = "http://cran.us.r-project.org")

# load the package
library(data.table)
```


## Format
The general format is `DT[I, J, BY]` which means: "Take DT, subset rows using *I*, then calculate *J* grouped by *BY*"

### Create a data.table
```{r, }
library(data.table) 

set.seed(45L)

DT <- data.table(V1=c(1L,2L),
                 V2=LETTERS[1:3], 
                 V3=round(rnorm(4),4),
                 V4=1:12)

DT

```

### Subsetting rows using `I`
```{r, }
#Subsetting rows by numbers.
DT[3:5,] #or DT[3:5]  #Selects third to fifth row.
```

Use column names to select rows in `I` based on a condition using fast automatic indexing. Or for selecting on multiple values:
DT[column %in% c("value1","value2")], which selects all rows that have value1 or value2 in column.

```{r, }
#Selects all rows that have value A in column V2.
DT[ V2 == "A"] 

# Select all rows that have the value A or C in column V2.
DT[ V2 %in% c("A","C")] 
```


### Manipulating on columns in `J`

Select one column in `J`
```{r, }
#Column V2 is returned as a vector.
DT[,V2] 
```

Select several columns in `J`.
```{r, }
#Columns V2 and V3 are returned as a data.table.
DT[,.(V2,V3)]
```

`.()` is an alias to `list()`. If `.()` is used, the returned value is a data.table. If `.()` is not used, the result is a vector.

Call functions in `J`:
```{r, }
#Returns the sum of all [1] 18 elements of column V1 in a vector.
DT[,sum(V1)]  
```

Computing on several columns. 
```{r, }
#Returns the sum of all V1 V2 elements of column V1 and the standard deviation of V3 in a data.table.
DT[,.(sum(V1),sd(V3))] 
```

Assigning column names to computed columns.
```{r, }
#The same as above, but with new names.
DT[,.(Aggregate = sum(V1), Sd.V3 = sd(V3))] 
```

Columns get recycled if different length.
```{r, }
#Selects column V1, and compute std. dev. of V3, which returns a single value and gets recycled
DT[,.(V1, Sd.V3 = sd(V3))]
```

Multiple expressions can be wrapped in curly braces.
```{r, }
#Print column V2 and plot V3.
DT[,{
  print(V2)
  plot(V3)
  NULL
  }]
```


### Doing `J` `BY` group
Doing j by group:
```{r, }
#Calculates the sum of V4, for every group in V1
DT[,.(V4.Sum = sum(V4)),by=V1]
```

Doing j by several groups using `.()`:
```{r, }
#The same as above, but for every group in V1 and V2.
DT[,.(V4.Sum = sum(V4)),by=.(V1,V2)]
```

Call functions in `BY`:
```{r, }
#Calculates the sum of V4, for every group in sign(V1-1).
DT[,.(V4.Sum = sum(V4)),by=sign(V1-1)] 
```

Assigning new column names in `BY`:
```{r, }
#Same as above, but with a new name for the variable we are grouping by.
DT[,.(V4.Sum = sum(V4)), by=.(V1.01 = sign(V1-1))] 
```

Grouping only on a subset by specifying `I`. 
```{r, }
#Calculates the sum of V4, for every group in V1, after subsetting on the first five rows.
DT[1:5,.(V4.Sum = sum(V4)),by=V1] 
```

Using `.N` to get the total number of observations of each group.
```{r, }
#Count the number of rows for every group in V1.
DT[,.N, by=V1] 
```

### Adding/Updating columns `BY` reference in `J` using `:=`
Adding/updating a column by reference using `:=` in one line.
**Watch out:** extra assignment (DT <- DT[...]) is redundant.
```{r, }
#Column V1 is updated by what is after :=.
DT[, V1 := round(exp(V1),2)]
```

Adding/updating several columns by reference using `:=`:
```{r}
# Column V1 and V2 are updated by what is after :=.
DT[, c("V1","V2") := list(round(exp(V1), 2), LETTERS[1:12])]
```


Using functional `:=`:
```{r, }
#Another way to write the same line as above this one, but easier to write
# comments side-by-side. Also, when [] is added the result is printed to the screen

DT[, ':=' (V1 = round(exp(V1),2), V2 = LETTERS[1:12])][]
```

Remove a column instantly using `:=`:
```{r, }
#Removes column V1
DT[, V1 := NULL]
```

Remove several columns instantly using `:=`:
```{r, }
#Removes columns V1 and V2.
DT[, c("V1","V2") := NULL]
```

Wrap the name of a variable which contains column names in parenthesis to pass the contents of that variable to be deleted:
```{r, }
Cols.chosen = c("A","B")

#Watch out: this deletes the column with column name Cols.chosen. 
DT[, Cols.chosen := NULL]

#Deletes the columns specified in the variable Cols.chosen (V1 and V2)
DT[, (Cols.chosen) := NULL]
```


## Example
Using basic exploratory analyses:

1. Plot the trend for number of cases in Coconino county and the state of Arizona, 
2. Show which counties and which states have passed their COVID-19 peak.
 
 
**Hint**:You can obtain the main dataset containing number of COVID-19 cases in the US from [this link](https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_confirmed_US.csv)

```{r}
library(data.table)

#download covid data
covid19_url <- 'https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_confirmed_US.csv'

# create an temporary file path to save the file
covid19_file <- tempfile(fileext = '.csv', pattern = basename(covid19_url))

#download the file
download.file(url = covid19_url, destfile = covid19_file)

#load the file as a 
covid <- fread(covid19_file)
# covid

#reorganizing the data from columns to rows
covid <- melt(covid, id.vars = 1:11, variable.name = 'date', value.name = 'count')
covid

#converting the date format
covid[, Date := as.Date(date, format = '%m/%d/%y')]
covid$date <- NULL

colnames(covid)
str(covid)

#plot covid cases in Coconino county, AZ
covid[Combined_Key == 'Coconino, Arizona, US', plot(Date, count)]

#define a colujmn for New Cases
covid[, new_cases := c(NA, diff(count)), Combined_Key]
covid[Combined_Key == 'Coconino, Arizona, US', plot(Date, new_cases)]

#plot covid cases in New York City
covid[Combined_Key == 'New York City, New York, US', plot(Date, new_cases)]

#group by Combined_Key
covid[, max_new_cases := max(new_cases, na.rm = TRUE), Combined_Key]

#show most recent data
covid[Date==Sys.Date()-1, ]

# print the names of the counties where number of cases is smaller than the maximum for that county
covid[(Date==Sys.Date()-1) & new_cases < max_new_cases, .(Combined_Key)]

#create a new table for states
covid_states <- covid[Province_State%in%state.name, 
                      .(state_new_cases = sum(new_cases)),
                      .(State = Province_State, Date)]
covid_states

#plot Arizona cases
covid_states[State=='Arizona', plot(Date, state_new_cases)]

# find maximum for each state
covid_states[, state_max := max(state_new_cases, na.rm = TRUE), State]

# when state's peak occured and sort states names by the peak's date
covid_states[state_new_cases==state_max, 
             .(state_max_date = min(Date)),
             State][order(state_max_date)]

# print the names of the states where number of cases is larger than the maximum for that state
covid_states[(Date==Sys.Date()-1)&state_new_cases>=state_max, .(State, state_new_cases)]

#plot the trend for the country
covid_usa <- covid[, .(Count = sum(new_cases)), .(Date)]

covid_usa[, plot(Date, Count)]

```

## More on `data.tables`:
- [R For Data Science Cheat Sheet](https://s3.amazonaws.com/assets.datacamp.com/blog_assets/datatable_Cheat_Sheet_R.pdf)
- [Data Transformation with data.table](https://www.beoptimized.be/pdf/R_Data_Transformation.pdf)
- Interactive course: [Data Analysis in R, the data.table Way](https://learn.datacamp.com/courses/data-table-data-manipulation-r-tutorial)


## Survey

<iframe src="https://docs.google.com/forms/d/e/1FAIpQLScK9ZS8WhTCZ2BElAOy0QJu9m0ChBAbOqy0ektf62Q8eOL1Tw/viewform?embedded=true" width="800" height="1000" frameborder="0" marginheight="0" marginwidth="0">Loading…</iframe>
